Efficiently summarizing relationships in large samples: a general duality between statistics of genealogies and genomes

### 2020-04-30 submit/cover_letter.tex
cover letter

    We are writing to submit our manuscript, entitled
    \emph{Efficiently summarizing relationships in large samples: a general
        duality between statistics of genealogies and genomes},
    for consideration for publication in \textit{Genetics}.

    An important part of the paper is that it introduces fast methods for computation
    of population genetic statistics from large numbers of genomes using tree sequences,
    available through the tested and validated python package \texttt{tskit}.
    However, that's not the main point ---
    if it was, we'd be submitting to a more bioinformatics-focused journal. 
    It is well-known that population genetics statistics say something about the underlying genealogies,
    although it is not common for researchers to explicitly discuss this.
    The bigger point of our manuscript is to describe a general framework that makes it clear
    precisely what aspect of the underlying genealogies is described by each statistic,
    under the infinite-sites model of mutation,
    and to provide methods to compute these statistics of tree shape as well.
    We think this makes population genetics statistics conceptually cleaner,
    but has some other possible benefits, besides speed:
    (1) we make it easy to invent and implement new statistics;
    (2) the framework allows separation of mutational from demographic noise;
    and (3) if unbiased tree sequences can be inferred from genomic data,
    summarizing the trees themselves provides a descriptive method
    insensitive to variation in substitution rate or perhaps even marker ascertainment.
    The last is dependent on testing and improvement of tree sequence inference,
    but would be tremendously useful, if it works out.

    We have put a lot of effort into making the paper accessible to the readership of \textit{Genetics}.
    The paper begins with a careful treatment of the theoretical framework and many examples,
    then illustrates points with simulation and a tree sequence inferred from 1000 Genomes data
    (by Speidel et al, 2019),
    and finally describes the fundamental algorithm and compares computational efficiency
    to other methods.
    The definitions and framework might seem lengthy,
    but in our assessment they are necessarily so:
    there are many false paths that intuition can lead even experienced theoreticians down,
    and choices we have made in our framework that might seem strange at first
    turn out to be natural once carefully considered.

    We are enthusiastic about the potential impact of this paper
    and its interest to the readers of \textit{Genetics}.
    We hope that you agree.

\closing{Sincerely,}

>>>>

We are writing with great joy and the final version of our accepted manuscript,
``Efficiently summarizing relationships in large samples: a general duality between statistics of genealogies and genomes''.
We have addressed both of Reviewer 2's final suggestions,
by adding an explanatory note to Figure 1's caption, and deleting the word "significant",
which didn't add anything to the sentence it was in.
No other changes have been made,
other than moving the \LaTeX over to the Genetics template.

We have not added section titles for ``Materials and Methods'' or ``Results'',
since we don't feel those are appropriate for our theoretically-oriented paper.
We hope this is OK with you,
as we see other fine Genetics papers have not included these section headings
(e.g., Jain \& Stephan 2017, \url{https://www.genetics.org/content/206/1/389}).
But, if you'd prefer we'll gladly put them in --- just let us know.

\closing{Thanks very much,}
